Normal States Training for High Accuracy Event Detection

### 2016-06-16 paper/ieeeFormat.tex
add ieee format version

\documentclass{sig-alternate-05-2015}
\usepackage{subfigure}
\usepackage{enumitem}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{bm}

@@

%\makeatletter
%\def\@copyrightspace{\relax}
%\makeatother

@@

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
%\doi{10.475/123_4}
\doi{**.***/***}

% ISBN
%\isbn{123-4567-24-567/08/06}
\isbn{***-****-**-***/**/**}

%Conference
%\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

%\acmPrice{\$15.00}

%
% --- Author Metadata here ---
%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

@@

%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\begin{comment}
\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\o}rv{\"a}ld Group}\\
       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Lawrence P. Leipuner\\
       \affaddr{Brookhaven Laboratories}\\
       \affaddr{Brookhaven National Lab}\\
       \affaddr{P.O. Box 5000}\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor Sean Fogarty\\
       \affaddr{NASA Ames Research Center}\\
       \affaddr{Moffett Field}\\
       \affaddr{California 94035}\\
       \email{fogartys@amesres.org}
% 6th. author
\alignauthor Charles Palmer\\
       \affaddr{Palmer Research Laboratories}\\
       \affaddr{8600 Datapoint Drive}\\
       \affaddr{San Antonio, Texas 78229}\\
       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
\end{comment}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
In the news value theory, the \textit{news unexpectedness} expects the journalists to report the events that are different from the routine things, a.k.a., the normal states. 
For humanbeing, normal states are knowledge learned from news streams and the external environment, and can describe what happened and help to identify what is happening.
In this paper, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumalation of happened things. 
In \textsc{NSDetector}, 1) balanced for effectiveness and efficiency, normal states are trained as topical words and their frequencies; 2) historical topical word frequencies are initialized from knowledge base with chi-squared test; 3) topical word frequencies on targeted corpus are maintened by KB-Prior-LDA, using the normal states in knowledge base as prior; 4) events are detected by monitoring the change of topical word frequencies. 
Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
And further experiments on \textit{reddit} and \textit{arXiv} also demonstrate that \textsc{NSDetector} can be easily adapted on other cyberspace datasets.
%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well. 
\end{abstract}

@@

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc{Mathematics of computing~Bayesian computation}
\ccsdesc{Mathematics of computing~Gibbs sampling}
\ccsdesc{Information systems ~ Data analytics}
\ccsdesc{Information systems ~Data stream mining}

%
% End generated code
%

%
%  Use this command to print the description
%
\printccsdesc

% We no longer use \terms command
%\terms{Theory}

\keywords{normal states initialization and maintenance; event detection;}

@@

\begin{figure}
    \label{fig:modelDesc}
    \includegraphics[height=7.0cm]{img/systemExample.pdf}
    \caption{\textsc{NSDetector}'s process flow, taking \textbf{military} related events in cyberspace as an example. \textsc{FullReader} initializes the normal states as topical word frequencies from full history information about military, updates them further at the specific corpus day by day, and detects events finally.}
\end{figure}

@@

\section{Proposed Method}
\subsection{Initialization of Normal States}
\textbf{User profile.} User usually describes herself or himself by a piece of short text on microblog platform.
This short text can be a continuous string or an array of hash tags, e.g., "\textit{Co-founder of Twitter, Medium, and now Co-founder and CEO of Askjelly.com}" of Biz Stone or "\textit{\#Cloud}, \textit{\#YARN}" of @hadoopchina.
Though it's easy to estimate Biz Stone's interests by his self-description text, it's not always capable of doing so because some users' are very short.
To overcome this limitation, we define \textbf{user profile} \(\bm{p_u}\) as combining user \(u\)'s self-description text with the texts provided by \(u\)'s followings. 
Taking Biz Stone as an example, he follows 696 accounts, in which there are 60 founders, 27 CEOs, 21 Google related, and 9 medium related accounts, etc. 
This example demonstrates that user profile \(p_u\) can be augmented by gathering the followings' information.

@@

\textbf{Event.} We define the event in the given time window \(t\) as the set of tweets denoted by \( \{ \bm{w_{te}}\}\).
The event related tweets in set \( \{ \bm{w_{te}}\}\)  hold two properties: (1) it is different from user \(u\)'s long term interests and (2) it is similar with other tweets in the set.
The task of event detection is to find out all the events in corpus.
Different methods treat the above properties in different ways: LSH based methods\cite{petrovic2010streaming} treat the difference and simliarity in word vector space; while the topic model based methods\cite{timeUserLDA2012finding} take the semantic meaning into consideration.
Under the framework of topic model, we divide the topics into user interest related topics and bursty event related topics, and further promote an online learning model UMIETM.
\subsection{Normal States' Initialization}
%TODO
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{img/normalStatesFromHistoryInfo.pdf}  
    \caption{Illustration on how to train normal states from wikipedia,( an approximation to the full history information).}
    \label{fig:modelDesc}
\end{figure}

\textbf{HITS step.}
After the above step, we obtain PageRank scores for either queries or candidate replies. To propagate such information to the other side in the query-reply bipartite graph, we perform another random walk with links between queries and replies representing the structural information of hubs and authorities. %To incorporate prior information (obtained in the PageRank step) of queries and replies, we adopt a HITS variant in \citeauthor{deng2009generalized}~\shortcite{deng2009generalized}, called Co-HITS.

Formally, the bipartite graph $G=(V,E)$ has vertexes  $V=\{V_q \cup V_r\}$, where $V_q$ are queries and $V_r$ are replies. We define the weight matrix by a relevance scoring function $\phi(q,r)$ between queries and replies. $\phi(\cdot,\cdot)$ was learned via a \textit{learning-to-rank} model similar to ~\shortcite{burges2005learning} with rich features including textual similarity, translation models, as well as {\tt word2vec} word embeddings \cite{mikolov2013distributed}. In other words, $\phi(\cdot,\cdot)$ returns the relatedness between a query and a reply in the range $(0,1)$.

Moreover, since we would like to make use of PageRank scores for queries or replies, the HITS links are judged by not only the static relevance score $\phi(\cdot,\cdot)$, but also the information given by PageRank. To be concrete, the (unnormalized) weight matrix is given by either
\begin{equation}
\text{\quad \quad\quad\quad\!}\tilde{\mathbf W}_{ij} = \phi(q_i, r_j)\cdot q_i\quad\quad\quad\text{(query$\rightarrow$reply)}
\label{eqn:w1}
\end{equation}
\begin{equation}
\text{or\quad\quad\quad} \tilde{\mathbf W}_{ij} = \phi(r_i, q_j)\cdot {r}_i\quad\quad\quad\text{(reply$\rightarrow$query)}
\label{eqn:w2}
\end{equation}
Here, $q_i$ and $r_i$ are the \textit{i}-th element in the vectors $\mathbf q$ and $\mathbf r$, which are obtained in the PageRank phase by Equations~\ref{eqn:pagerank1}--\ref{eqn:pagerank2}. If information is propagated from queries to replies, we use the former equation for weight update, and \textit{vice versa}.

The mutual-reinforcing relationship of hub and authority scores can be expressed in matrix representation as follows.
\begin{align}
\mathbf{x}^{(i+1)} &= \alpha_x\cdot \big[\tilde{\mathbf W}\big]\,\mathbf{y}^{(i)}+(1-\alpha_x)\cdot \hat{\mathbf{x}}\label{eqn:HITS2}\\
\mathbf{y}^{(i+1)} &= \alpha_y\cdot \left[\big[\tilde{\mathbf W}\big]^\top\right]\mathbf{x}^{(i)}+(1-\alpha_y)\cdot\hat{\mathbf{y}} \label{eqn:HITS1}
\end{align}
where $\mathbf x$ is query scores, $\mathbf y$ reply scores; superscripts denote the number of local iterations in HITS update.
Each column of the weights is normalized to be a valid probability. Moreover, to compute the weight for $\mathbf{y}$, the matrix $\mathbf{\tilde W}^\top$ should be first row-normalized (given by $[\mathbf{\tilde W}]^\top$); otherwise, the effect of the prior $q_i$ in Equation~\ref{eqn:w1} is ruled out by column normalization.
Notice that the transition matrix is fixed in one step of HITS, but they may also change as our algorithm proceeds like the PageRank step.

@@

\begin{enumerate}[noitemsep]
    \item for each topic \(k \in \{1,\cdots,K\}\)，
    \begin{enumerate}
        \item word distribution on the topic \(\phi_k \sim Dirichlet(\beta+\tau_k)\).
    \end{enumerate}
    \item for each document \(d \in D\)，
    \begin{enumerate}
        \item topic distribution on the document \(\theta_d \sim Dir(\alpha)\)
        \item for each word index \(n \in \{1,\cdots,N_d\}\)，
        \begin{enumerate}
            \item word's topic assignment \(z_{dn} \sim Multinomial(\theta_d)\)，
            \item word \(w_{dn} \sim Multinomial(\phi_{z_{dn}})\)
        \end{enumerate}
    \end{enumerate}
\end{enumerate}

\begin{equation}
\label{eq:wikiPrior}
\begin{aligned}
\tau_{kv}=
\left\{ \begin{aligned}
W \frac{f_{kv}}{\sum_{v\in S_{kv}}f_{kv}} &,v\in S_{k} \\
0&,v \notin S_{k}\\
\end{aligned}\right.
\end{aligned}
\end{equation}

\begin{equation}
\label{eq:LDAgibbs}
\begin{aligned}
&p(z_{dn}=k|w_{dn}=v,z_{\neg{dn}},w_{\neg{dn}},\alpha,\beta,\tau)\\
&\ \ \propto (n_{dk}+\alpha)\frac{n_{kv}+\tau_{kv}+\beta}{n_{k,.}+\tau_{k,.}+V\beta}
\end{aligned}
\end{equation}
\begin{comment}
\begin{algorithm}[H]
    \caption{UPIETM batch learning algorithm} %title
    \label{alg:UPIETMbatch} %label
    \begin{algorithmic}[1] %this 1 means the showing of line number in algorithm
    \STATE initiate the topic label and the statistics
    \FOR {\(i=1:I_1\)}
        \FOR{\(u\) in  user set U}
            \FOR{\(n\) = \(1:P_u\)}
                \STATE sample profile's hidden topic \(s_{un}\) by (\ref{timeUserTagLDAIVsamplingForS})
                \STATE update \(s_{un}\), \(c^{(p)}_{u,k}\) and \(c^{(p)}_{k,v}\)
            \ENDFOR%end of n
        \ENDFOR%end of u
    \ENDFOR%end of i
    \FOR{iteration \(i=1:I_2\)}
        \FOR{\(t=1:T\)}
            \FOR{\(u\) in  user set \(U_t\)}
                \FOR{\(d\) = \(1: D_u\) }
                    \STATE{sample \(y_{ud}\) and \(z_{ud}\) by (\ref{timeUserTagLDAIVJointSamplingForY0Z}), (\ref{timeUserTagLDAIVJointSamplingForY1Z}) }
                    \IF{\(y_{ud}=0\)}
                        \STATE{update \(z_{ud}\), \(y_{ud}\), \(c^{(0)}_u\), \(c^{(0)}_{u,k}\), \(c^{(0)}_{k,v}\)}
                    \ELSE
                        \STATE{update \(z_{ud}\), \(y_{ud}\), \(c^{(1)}_u\), \(c^{(1)}_{t,k}\), \(c^{(1)}_{t,k,v}\)}
                    \ENDIF
                    \FOR{\(n\) in \(1,\cdots,N_{ud}\)}
                        \STATE{sample \(x_{udn}\) by (\ref{timeUserTagLDAIVsamplingX0}), (\ref{timeUserTagLDAIVsamplingX1}})
                        \IF{\(x_{udn}=0\)}
                            \STATE{update \(x_{udn}\), \(M^{\rho}_0\), \(c^{(B)}_v\)}
                        \ELSE
                            \STATE{update \(x_{udn}\), \(M^{\rho}_1\), \(c^{(0)}_{k,v}\), \(c^{(1)}_{t,k,v}\) }
                        \ENDIF
                    \ENDFOR%end of n
                \ENDFOR%end of d
            \ENDFOR%end of u
        \ENDFOR%end of t
    \ENDFOR%end of i
    \end{algorithmic}
\end{algorithm}
\end{comment}

>>>>

%\documentclass{sig-alternate-05-2015}
\documentclass[conference,compsoc]{IEEEtran}
\usepackage{comment}
\usepackage{subfigure}
\usepackage{enumitem}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
%\usepackage{algorithm}
\usepackage{bm}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{amsmath} 
\usepackage{amssymb}

@@

@@

@@

\maketitle
\begin{abstract}
In the news value theory, the \textit{news unexpectedness} expects the journalists to report the events that are different from the routine things, a.k.a., the normal states. 
For human being, normal states are knowledge learned from news streams and the external environment, and can describe what happened and help to identify what is happening.
In this paper, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of happened things. 
%TODO
In \textsc{NSDetector}, 1) balanced for effectiveness and efficiency, normal states are trained as topical words and their chi-squared scores, and initialized by knowledge base; 2) topical word frequencies on targeted corpus within the time window are learned by NS-Prior-LDA, using the normal states as prior; 3) events are detected by monitoring the change of topical word frequencies; 4) normal states are further maintained by detected events incrementally.
Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
And further experiments on \textit{reddit} also demonstrate that \textsc{NSDetector} can be easily adapted on other cyberspace datasets.
%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well. 
\end{abstract}

@@

@@

\begin{figure}
    \label{fig:modelDesc}
    \includegraphics[width=1.0\columnwidth]{img/NSDetectorExample.pdf}
    \caption{\textsc{NSDetector}'s process flow, taking \textbf{military} related events in cyberspace as an example. \textsc{FullReader} initializes the normal states as topical word frequencies from full history information about military, updates them further at the specific corpus day by day, and detects events finally.}
\end{figure}

@@

\section{Proposed Method}
\begin{algorithm}
\caption{Overview of \textsc{NSDetector}}
\label{alg:overviewNSDetector}
\KwIn{Knowledge Base's structure \(G^{(0)}\), \(G^{(1)}\), and content \(G^{(2)}\), }
\KwOut{Events}
\(n_{k,t}\)=number of connected component in \(\mathcal{G}_{k,t}\)\\
\For{\(n \in \{ n_{k,t}, \cdots, |\mathcal{G}_{k,t}|\}\) }{
    \(\mathcal{C}_{k,t}=SpectralClustering(\mathcal{G}_{k,t},n)\)\\
    \If{\(min_{i\in \{1,\cdots,n\}} Density(\mathcal{C}_{k,t,i},\mathcal{G}_{k,t})>\tau\)}{
        return \(\mathcal{C}_{k,t}\)
    }
}
\end{algorithm}

\subsection{Initialization of Normal States}
\textbf{User profile.} User usually describes herself or himself by a piece of short text on microblog platform.
This short text can be a continuous string or an array of hash tags, e.g., "\textit{Co-founder of Twitter, Medium, and now Co-founder and CEO of Askjelly.com}" of Biz Stone or "\textit{\#Cloud}, \textit{\#YARN}" of @hadoopchina.
Though it's easy to estimate Biz Stone's interests by his self-description text, it's not always capable of doing so because some users' are very short.
To overcome this limitation, we define \textbf{user profile} \(\bm{p_u}\) as combining user \(u\)'s self-description text with the texts provided by \(u\)'s followings. 
Taking Biz Stone as an example, he follows 696 accounts, in which there are 60 founders, 27 CEOs, 21 Google related, and 9 medium related accounts, etc. 
This example demonstrates that user profile \(p_u\) can be augmented by gathering the followings' information.

@@

\textbf{Event.} We define the event in the given time window \(t\) as the set of tweets denoted by \( \{ \bm{w_{te}}\}\).
The event related tweets in set \( \{ \bm{w_{te}}\}\)  hold two properties: (1) it is different from user \(u\)'s long term interests and (2) it is similar with other tweets in the set.
The task of event detection is to find out all the events in corpus.
Different methods treat the above properties in different ways: LSH based methods\cite{petrovic2010streaming} treat the difference and simliarity in word vector space; while the topic model based methods\cite{timeUserLDA2012finding} take the semantic meaning into consideration.
Under the framework of topic model, we divide the topics into user interest related topics and bursty event related topics, and further promote an online learning model UMIETM.
\subsection{Normal States' Initialization}
\begin{algorithm}
\caption{Normal States' Initialization from Knowledge Base}
\label{alg:normalStatesInit}
\KwIn{Taxonomy's Directed Acyclic Graph \(G^{(0)}\), Category-Page Bipartite Graph \(G^{(1)}\), Page-Content Bipartite Graph \(G^{(2)}\), topic related category node \(c\)}
\KwOut{Normal states \(\bm{f}_c\) on topic \(c\)}
\(Pages(c)\leftarrow \varnothing\)\\
\(SuccessorNodes(c) \leftarrow \) Breadth-first-search(\(G^{(0)},c\))\\
\For{\(node \in SuccessorNodes(c)\)}{
    \(Pages(c) \leftarrow Pages(c) \cup G^{(1)}.neighbours(node)\)\\
}
\(WordFrequencyTable(c) \leftarrow \) do word count on the text contents of \(Pages(c)\) \\
\(WordFrequencyTable(All) \leftarrow \) do word count on the text contents of all pages in \(G^{(2)}\).\\
\For{word \(w\) in WordFrequencyTable(All).keys()}{
    \(\tau_{c,w} \leftarrow \) \(w\)'s chi-square score on \(WordFrequencyTable(c)\) and \(WordFrequencyTable(All)\).
}
\Return{\(\bm{f}_c\)}
\end{algorithm}

\cite{faralli2015large} propose the Twixonomy Graph.

%TODO
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{img/initializationExample.pdf}  
    \caption{Illustration on how to train normal states from wikipedia,( an approximation to the full history information).}
    \label{fig:modelDesc}
\end{figure}

@@

\begin{table}[!htbp]
\begin{tabular}{l}
1. Draw corpus prior distribution \(\bm{m} \sim Dir(\alpha \bm{u})\), where \(\bm{u}\)\\
 \ \ \ \ is the uniform distribution. \\
2. For each topic \(k \in \{1,\cdots,K\}\),\\
\ \ \ \ (a) word distribution on the topic \(\bm{\phi_k} \sim Dir(\bm{\beta}+ \bm{\tau_k})\). \\

3. For each document index \(d \in \{1,...,D\}\), \\
\ \ \ \ (a) topic distribution on the document \(\theta_d \sim Dir(\bm{m})\), \\
\ \ \ \ (b) for each word index \(n \in \{1,\cdots,N_d\}\),\\
\ \ \ \ \ \ \ \ i. word's topic assignment \(z_{dn} \sim Multinomial(\theta_d)\), \\
\ \ \ \ \ \ \ \ ii. word \(w_{dn} \sim Multinomial(\phi_{z_{dn}})\). \\
\end{tabular}
\end{table}

\begin{equation}
\label{eq:wikiPrior}
\begin{aligned}
\tau_{kv}=
\left\{ \begin{aligned}
\lambda \frac{f_{kv}}{\sum_{v\in S_{kv}}f_{kv}} &,v\in S_{k}\ and  \ k \leq K_{\bm{KB}} \\
0&,v \notin S_{k} \ or \ k > K_{\bm{KB}} \\
\end{aligned}\right.
\end{aligned}
\end{equation}

\begin{equation}
\label{eq:initProbability}
\begin{aligned}
\hat{q}_{k|v}=
\left\{ \begin{aligned}
\frac{\tau_{kv}}{\sum_{k=1}^{K}\tau_{kv}} &,\sum_{k}\tau_{kv}>0 \\
0&, \sum_{k}\tau_{kv}=0 \ and \ k \leq K_{\bm{KB}} \\
1/(K-K_{\bm{KB}})&,\sum_{k}\tau_{kv}=0 \ and \ k > K_{\bm{KB}}
\end{aligned}\right.
\end{aligned}
\end{equation}

\begin{equation}
\label{eq:KBPriorLDAgibbs}
\begin{aligned}
&p(z_{dn}=k|w_{dn}=v,z_{\neg{dn}},w_{\neg{dn}},\alpha,\beta,\tau)\\
&\ \ \propto (n^{(d)}_{dk}+\alpha m_k)\frac{n^{(w)}_{kv}+\tau_{kv}+\beta}{n^{(w)}_{k,.}+\tau_{k,.}+V\beta}
\end{aligned}
\end{equation}

\begin{algorithm}
\caption{NS-Prior-LDA Learning Algorithm}
\label{alg:gibbsSamplingKBPriorLDA}
\KwIn{Document sequences \(\bm{w_{1:D}}\), and normal states \(\bm{f}_{1:K_{\bm{KB}}}\)}
\KwOut{The sufficient statistics \(\bm{n^{(d)}}\), \(\bm{n^{(w)}}\)}
\medskip
\tcc{Initialization of NS-Prior-LDA Learning}
\For{\(d=1:D\)}{
    \For{\(n=1:N_d\)}{
        \(v=w_{dn}\), sample \(z_{dn}=k\) accroding to Eq(\ref{eq:wikiPrior})(\ref{eq:initProbability}).\\
        Update the sufficient statistics \(n^{(d)}_{d,k}\), \(n^{(w)}_{k,v}\).\\
            }
        }
\medskip
\For{\(i= 1:I\)}{
    \tcc{E-Step of NS-Prior-LDA Learning}
    \For{\(i=1:I_E\)}{
        \For{\(d=1:D\)}{
            \For{\(n=1:N_d\)}{
                Set \(v=w_{dn}\), and reset the sufficient statistics \(n^{(d)}_{d,z_{dn}}\), \(n^{(w)}_{z_{dn},v}\).\\
                Resample \(z_{dn}=k\) accroding to Eq(\ref{eq:wikiPrior})(\ref{eq:KBPriorLDAgibbs}).\\
                Update the sufficient statistics \(n^{(d)}_{d,k}\), \(n^{(w)}_{k,v}\).\\
            }
        }
    }
    \medskip
    \tcc{M-Step of NS-Prior-LDA Learning}
    Optimize \(\alpha \bm{m}\) by the fixed-point iteration\cite{wallach2008structured}. 
}
\Return{\(\bm{n^{(d)}}\), \(\bm{n^{(w)}}\)}
\end{algorithm}

\cite{wallach2008structured}\footnote{\url{https://github.com/mimno/Mallet/blob/master/src/cc/mallet/types/Dirichlet.java}}
